\documentclass[10pt, letterpaper]{article}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage[top=0.4in, bottom=0.4in, left=0.4in, right=0.4in]{geometry}
\usepackage{mathptmx}
\usepackage[expansion=false]{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{ragged2e}

% ── Colours ───────────────────────────────────────────────────────────────────
\definecolor{primaryblue}{RGB}{27,58,107}   % professional navy blue

% ── Hyperlink styling ─────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=primaryblue,
  linkcolor=black
}

% ── No page number ─────────────────────────────────────────────────────────────
\pagestyle{empty}

% ── Section heading style: bold, full-width rule below ────────────────────────
\titleformat{\section}
  {\bfseries\Large\color{primaryblue}}
  {}
  {0em}
  {}
  [\vspace{2pt}\titlerule\vspace{3pt}]

\titlespacing{\section}{0pt}{6pt}{3pt}

% ── Bullet list settings ──────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.4em,
  itemsep=2pt,
  parsep=0pt,
  topsep=3pt,
  label=\textbullet
}

% ── Column separator ──────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ── Helper: job entry header ──────────────────────────────────────────────────
\newcommand{\jobentry}[2]{%
  \noindent\textbf{#1}\hfill\small #2\par
}

\newcommand{\company}[1]{%
  \noindent\textit{#1}\par\vspace{2pt}
}

\newcommand{\projentry}[1]{%
  \vspace{4pt}\noindent\textbf{#1}\par\vspace{1pt}
}

\newcommand{\eduentry}[3]{%
  \noindent\textbf{#1,} \textit{#2}\hfill\small #3\par\vspace{3pt}
}

\newcommand{\skillrow}[2]{%
  \item \textbf{#1:} #2
}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}
% ══════════════════════════════════════════════════════════════════════════════

% ─────────────────────────────────────────────────────────────────────────────
%  HEADER
% ─────────────────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{primaryblue} SAHIL JAIN}\\[4pt]
  \href{https://www.linkedin.com/in/imsahiljain/}{linkedin.com/in/imsahiljain} \textbar{}
  \href{https://imsahiljain.in}{imsahiljain.in} \textbar{}
  \href{https://github.com/im-sahiljain}{github.com/im-sahiljain} \textbar{} 
  \href{mailto:mr.sahiljain14@gmail.com}{mr.sahiljain14@gmail.com} \textbar{} 
  \href{tel:PHONE_NUMBER_PLACEHOLDER}{PHONE_NUMBER_PLACEHOLDER} \textbar{} 
  \small\color{primaryblue} India
\end{center}

\vspace{6pt}
%\noindent\rule{\textwidth}{0.8pt}
%\vspace{8pt}

% ─────────────────────────────────────────────────────────────────────────────
%  PROFESSIONAL SUMMARY
% ─────────────────────────────────────────────────────────────────────────────
\section*{PROFESSIONAL SUMMARY}
\vspace{-2pt}

Frontend-focused Full Stack Developer with hands-on experience building scalable, high-performance React.js and Next.js applications. Skilled in JavaScript (ES6+), Redux state management, component design, and RESTful API development and integration. Experienced in UI/UX design translation, browser-based debugging, performance testing frameworks (Jest), and full software development life cycle including coding standards, source control (Git), testing, and deployment. Strong problem-solving abilities with a track record of delivering production-ready solutions in agile environments.

\vspace{4pt}

% ─────────────────────────────────────────────────────────────────────────────
%  TECHNICAL SKILLS
% ─────────────────────────────────────────────────────────────────────────────
\section*{TECHNICAL SKILLS}
\vspace{-2pt}

\begin{itemize}[leftmargin=1.4em, itemsep=3pt]
  \skillrow{React Ecosystem}{React.js, Redux Toolkit, React Hooks (useEffect, useCallback, useMemo)}
  \skillrow{Languages}{JavaScript (ES6+), TypeScript, HTML5, CSS3, Python}
  \skillrow{Testing \& Debugging}{Jest, Postman, Swagger, Browser DevTools}
  \skillrow{Backend / Databases}{Node.js, Express.js, MongoDB, MySQL, PostgreSQL, Axios, Django}
  \skillrow{UI Libraries}{Tailwind CSS, Ant Design, Material Design, ReCharts}
  \skillrow{DevOps \& Tools}{Git/GitHub, Docker, Linux, Figma, VS Code, Vercel, NPM}
  \skillrow{SDLC Practices}{Agile, Code Reviews, Coding Standards, Source Control Management}
\end{itemize}

\vspace{4pt}

% ─────────────────────────────────────────────────────────────────────────────
%  WORK EXPERIENCE
% ─────────────────────────────────────────────────────────────────────────────
\section*{WORK EXPERIENCE}
\vspace{-2pt}

\jobentry{Software Development Engineer}{Nov 2024 -- May 2026 \textbar{} Jaipur}
\company{\href{https://www.xyberiatech.com/}{Xyberia Technologies Private Limited}}

\begin{itemize}
  \item Architected and delivered a full-stack Next.js + React admin dashboard with JWT based authentication, RBAC, and dual-login systems, supporting 10+ client organizations with plan-based feature access.
  \item Engineered reusable, responsive React component library with API driven rendering; applied React.memo, useCallback, and useMemo to optimize re-render cycles reducing development effort by 20–25\% and improving UI consistency.
  \item Implemented Redux Toolkit for centralized state management across multi role workflows, following industry best practices for predictable state transitions and clean component separation.
  \item Designed scalable backend services using Node.js, Express.js, and MongoDB modeled 10+ collections and optimized queries with aggregation pipelines for multi user, multi role workflows.
  %\item Built and documented 100+ RESTful APIs using Django (Python) and Swagger, standardizing request/response schemas and HTTP conventions to improve maintainability and cross-team integration.
  \item Drove frontend performance optimization via code splitting, lazy loading, Webpack bundle analysis, and browser based debugging to identify and resolve bottlenecks, improving Core Web Vitals scores.
  \item Applied Agile practices and led structured code reviews to enforce coding standards, Git branching strategy, and SDLC best practices; collaborated with cross functional teams to convert requirements into technical designs.
\end{itemize}

\vspace{6pt}

%\jobentry{Full Stack Developer Intern}{Jun 2024 – Sep 2024 \textbar{} Chandigarh}
%\company{I-Monk}

%\begin{itemize}
%  \item Translated Figma designs into pixel-perfect, fully responsive React.js UIs with smooth cross-device compatibility, ensuring exceptional user experience and adherence to design specifications.
 % \item Built reusable, testable React components tailored to client requirements; integrated RESTful APIs using Axios and React Hooks, delivering 40\% increase in customer satisfaction through improved UI reliability.
  %\item Utilized Jest and browser-based debugging tools for performance testing and troubleshooting, ensuring robust, production-ready code.
  %\item Crafted detailed project documentation (Microsoft Docs, PowerPoint) covering design specs and development workflows, ensuring smooth handoff and project clarity.
%\end{itemize}

%\vspace{4pt}

% ─────────────────────────────────────────────────────────────────────────────
%  EDUCATION
% ─────────────────────────────────────────────────────────────────────────────
\section*{EDUCATION}
\vspace{-2pt}

\eduentry{M.Sc. in Computer Science}{Savitribai Phule Pune University}{Sep 2021 – Jul 2023 \textbar{} Pune}
\eduentry{Bachelor of Computer Applications}{Panjab University}{Jul 2018 – Jun 2021 \textbar{} Chandigarh}

\vspace{4pt}

% ─────────────────────────────────────────────────────────────────────────────
%  PROJECTS
% ─────────────────────────────────────────────────────────────────────────────
\section*{PROJECTS}
\vspace{-2pt}

\projentry{\href{https://orgcontrol.imsahiljain.in}{Org Control} \textbar{} Next.js · React · Redux Toolkit · TanStack Query · Zod}
\begin{itemize}
  \item Engineered a hybrid state management architecture by decoupling server side asynchronous data fetching (TanStack Query) from complex client side UI interactions (Redux Toolkit), drastically reducing unnecessary re renders.
  \item Established end-to-end type safety using TypeScript and Zod schema validation across API routes and forms; built a streaming AI Copilot that dynamically intercepts and contextually filters user queries based on active Redux session states.
\end{itemize}


\projentry{\href{https://feedbackdeskai.imsahiljain.in}{FeedBack Desk AI} \textbar{} Next.js · React · TypeScript · AI Integration}

\begin{itemize}
  \item Built a full-stack AI-powered customer feedback management platform using Next.js, React.js, TypeScript, and Redux; enabled real-time feedback collection, organization, and analysis across multiple products.
  \item Implemented AI-driven classification to auto-tag feedback by sentiment, category, and priority — significantly reducing manual triage time and supporting faster data-driven product decisions.
  \item Applied lazy loading, code splitting, and memoization for optimal performance; designed responsive, accessible UI components ensuring smooth UX across all screen sizes.
\end{itemize}

% \projentry{\href{https://whichethanol.imsahiljain.in/}{Which Ethanol} \textbar{} React.js · MongoDB · AI Validation}
% \begin{itemize}
%   \item Compiled and structured vehicle compatibility data for 30+ manufacturers and 50+ models from verified sources; stored in MongoDB with aggregation queries for fast compatibility lookups.
%   \item Built a clean, responsive React.js frontend for user-friendly browsing; applied AI-assisted validation to cross-check ethanol compatibility and improve dataset consistency.
% \end{itemize}

\end{document}